### 2014-09-24 ApTranscriptome_TR.Rmd
updates to script

```{r temperature_response_table, echo=FALSE, results='asis'}
# add row and column totals
tt3 <- rbind(tt2, colSums(tt2))
tt3 <- cbind(tt3, rowSums(tt3))
colnames(tt3)[6] <- "Total"
rownames(tt3)[6] <- "Total"
# move names into table
tt3 <- rbind(rownames(tt3), tt3)
tt3 <- cbind(rownames(tt3), tt3)
# name col/row by species
rownames(tt3) <- c("AcNC", "", "", "", "", "", "")
colnames(tt3) <- c("ApVT", "", "", "", "", "", "")

@@

(T_off.int.low.ttest <- t.test(Ar.int.T_off$T_off_low, A22.int.T_off$T_off_low))

```

@@

# table results
Ap.BP.ResTable <- GenTable(Ap.BP.GOdata, parentchild = Ap.BP.resultParentChild, topNodes = 10)
Ap.BP.ResTable
```

@@

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, md, qlslope, qlmean, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.union, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, file = "ms.RData")
```

>>>>

```{r temperature_response_table, echo=FALSE, results='asis'}
# add row and column totals
tt3 <- rbind(tt2, colSums(tt2))
tt3 <- cbind(tt3, rowSums(tt3))
colnames(tt3)[6] <- "Total"
rownames(tt3)[6] <- "Total"
# move names into table
tt3 <- rbind(rownames(tt3), tt3)
tt3 <- cbind(rownames(tt3), tt3)
# name col/row by species
rownames(tt3) <- c("AcNC", "", "", "", "", "", "")
colnames(tt3) <- c("**ApVT**", "", "", "", "", "", "")

@@

(T_off.int.low.ttest <- t.test(Ar.int.T_off$T_off_low, A22.int.T_off$T_off_low))
```

@@

# table results
Ap.BP.ResTable <- GenTable(Ap.BP.GOdata, parentchild = Ap.BP.resultParentChild, topNodes = 132)
Ap.BP.ResTable
```

@@

GSEA for genes that are *Intermediate* in A. carolinensis and *Low* or *Bimodal* in A. picea

```{r gsea_Ar_int_A22_lowbim, results = 'hide'}
# genes with *Intermediate* expression in Ar and *Low* in A22
Ar.int.A22.lowbim <- c(Ar.int.A22.low, Ar.int.A22.bim)
Ar.int.A22.lowbim.geneList <- rep(0, length = length(Ap.geneList))
names(Ar.int.A22.lowbim.geneList) <- names(Ap.geneList)
Ar.int.A22.lowbim.geneList[(which(names(Ar.int.A22.lowbim.geneList) %in% Ar.int.A22.lowbim))] <- 1
# check correct number of values set to 1
table(Ar.int.A22.lowbim.geneList)
# run GSEA
Ar.int.A22.lowbim.gsea <- gsea(genelist = Ar.int.A22.lowbim.geneList, geneID2GO = geneID2GO, plotpath = NA)
```

```{r gsea_Ar_int_A22_lowbim_cluster}
# similarity among enriched GO terms
Ar.int.A22.lowbim.gsea.term.sim <- termSim(Ar.int.A22.lowbim.gsea$GO.ID, Ar.int.A22.lowbim.gsea$GO.ID, ont = "BP", organism = 'fly')
# replace GO IDs with terms
rownames(Ar.int.A22.lowbim.gsea.term.sim) <- Ar.int.A22.lowbim.gsea$Term
colnames(Ar.int.A22.lowbim.gsea.term.sim) <- Ar.int.A22.lowbim.gsea$Term
# distance matrix
Ar.int.A22.lowbim.gsea.term.sim.hclust <- hclust(dist(Ar.int.A22.lowbim.gsea.term.sim))
plot(Ar.int.A22.lowbim.gsea.term.sim.hclust)
# report items in each cluster at height 1
(Ar.int.A22.lowbim.hclust.report <- GSEAReportClusters(Ar.int.A22.lowbim.gsea.term.sim.hclust, h = 1.2))
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, hsp_responsive, hsp_all, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, file = "doc/ms.RData")
```
